Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added NBR gender retro graph

```{r NBR gender prepan}

@@

```{r}

>>>>

```{r GLAD/EDGI gender retro}

@@

```{r NBR gender retro}

NBR.retro %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the NBR retro cohort",
       subtitle = paste("N =", dim(NBR.retro)[1]),
       x = "",
       y = "N participants")
